Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-20 ICML-submission/related-work.tex
Update related-work.tex
Changed frac to slash

The linear classification version of this problem is initially studied
by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed two computationally
inefficient algorithms that work in the weakly linearly separable setting, one
with a mistake bound of $O(K^2 d \ln(\frac{d}{\gamma}))$, the other with a
mistake bound of $\widetilde{O}(\frac{K^2}{\gamma^2} \ln T)$. The latter result
was later improved by \citet{Daniely-Helbertal-2013}, which gives a
computationally inefficient algorithm with a mistake upper bound of
$\widetilde{O}(\frac{K}{\gamma^2})$. In addition, the authors propose the
\textsc{Banditron} algorithm, a computationally efficient algorithm that has a
$O(T^{2/3})$ regret against the multiclass hinge loss in the general setting,
and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weakly linearly separable
setting.
In contrast to mild dependencies on the time horizon for mistake bounds of
computationally inefficient algorithms,
the polynomial dependence of \textsc{Banditron}'s mistake bound on the
time horizon is undesirable for problems with a long time horizon, in the
weakly linearly separable setting. One key open
question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can
design computationally efficient algorithms that achieve mistake bounds that
match or improve over those of inefficient algorithms. In this paper, we take a
step towards answering this question, showing that efficient algorithms with
mistake bounds quasipolynomial in $\frac 1 \gamma$ or quasipolynomial in $K$ can
be obtained.

>>>>

The linear classification version of this problem is initially studied
by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed two computationally
inefficient algorithms that work in the weakly linearly separable setting, one
with a mistake bound of 
$O(K^2 d \ln(d/\gamma))$,
the other with a
mistake bound of $\widetilde{O}((K^2/\gamma^2) \ln T)$. The latter result
was later improved by \citet{Daniely-Helbertal-2013}, which gives a
computationally inefficient algorithm with a mistake upper bound of
$\widetilde{O}(K/\gamma^2)$. 
In addition, the authors propose the
\textsc{Banditron} algorithm, a computationally efficient algorithm that has a
$O(T^{2/3})$ regret against the multiclass hinge loss in the general setting,
and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weakly linearly separable
setting.
In contrast to mild dependencies on the time horizon for mistake bounds of
computationally inefficient algorithms,
the polynomial dependence of \textsc{Banditron}'s mistake bound on the
time horizon is undesirable for problems with a long time horizon, in the
weakly linearly separable setting. One key open
question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can
design computationally efficient algorithms that achieve mistake bounds that
match or improve over those of inefficient algorithms. In this paper, we take a
step towards answering this question, showing that efficient algorithms with
mistake bounds quasipolynomial in $\frac 1 \gamma$ or quasipolynomial in $K$ can
be obtained.
